Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-06-03 analysis/sim/run_simpw.Rmd
updating simulation analysis

---
title: "Examining background gene lists using simulation - comparison of different enrichment techniques"
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
theme: cosmo
---

@@

SIMS=8
FRAC_DE=0.05
FC=1
N_REPS=5
DGE_FUNC="deseq2"
SUM_COUNT=3e7
VARIANCE=c(0.3,0.35,0.4)

>>>>

652 4---
title: "Examining background gene lists using simulation - comparison of different enrichment techniques"
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
theme: cosmo
---

@@

SIMS=16
FRAC_DE=0.05
FC=1
N_REPS=5
DGE_FUNC="deseq2"
SUM_COUNT=2e7
VARIANCE=c(0.3,0.35,0.4,0.45)
